\chapter{Introduction}

Nowadays the usage of technical devices has become irreplaceable. But with increasing
densification of devices comes network congestion: problems of
browsing the web during a train ride or a concert are apparent. Simply put, the current
location-based networking was not addressed for today's idea of massive content sharing. 
In order to face these problems Information-Centric Networking (ICN) was introduced. For
more information about ICN and all its existing architectures (Data-Oriented Network Architecture (DONA),
Content-Centric Networking (CCN), Publish-Subscribe Internet Routing Paradigm (PSIRP) and Network of Information (NetInf)) 
see \cite{netinf}.
The idea behind ICN is to shift the focus from hosts that serve a content to the actual objects that
are shared. More specifically, these Named Data Objects (NDO) shall no longer be coupled
to a host that is owning the content, but shall ideally be retrievable from \textit{anywhere}.

This report picks a proof-of-concept implementation of the usage of NetInf
(see \sect{netinf}), one out of four concepts that realize ICN. The software was
developed in the context of the 
\textit{Project Computer Science}\footnote{\url{http://www.it.uu.se/edu/course/homepage/projektDV/ht12}},
a course under the supervision of Olle G\"{a}llmo and in cooperation with Ericsson Research \cite{ericsson}
in 2012/2013. The goals set for this project are listed in \sect{goals}. 

The product itself consists of two separate parts developed by two development teams within the same project group. One is an Erlang \cite{erlang} implementation of a Name Resolution Service (NRS) with streaming capabilities.
The other product is a browser application called "Elephant" for Android \cite{android}  phones that takes advantage of NetInf services that
are based on OpenNetInf \cite{opennetinf}, an open source Java implementation of NetInf. 

Both products are described more in detail in \sect{product}. For a thorough understanding
of the implementation and extension of the current state, preliminaries and system architecture decisions are 
described in \sect{preliminaries} and \sect{architecture}. 
The performance of both products are evaluated in \sect{evaluation} and based on the results,
\sect{conclusions} discusses the future work and draws conclusions for the developed products. Finally, the appendix contains installation as well as maintenance instructions.
