\documentclass[11pt]{report}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{url}
\usepackage{epstopdf}
\usepackage{listings}
\usepackage{color}
\usepackage{ulem}

\renewcommand\bibname{References}

% reference commands
\newcommand{\fig}[1]{Figure ~\ref{fig:#1}}
\newcommand{\tab}[1]{Figure ~\ref{tab:#1}}
\newcommand{\sect}[1]{Section ~\ref{sec:#1}}

\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\parindent 0pt
\parskip 8pt

%Gummi|061|=)
\title{Project CS 2012 Product Report\\Uppsala University\\}

\author{Daniele Bacarella\\
		Jon Borglund\\
		Paolo Boschini\\
		Kiril Goguev\\
		Faroogh Hassan\\
		Marcus Ihlar\\
		Alexander Lindholm\\
		Knut Lorenzen\\
		Harold Mart\'{i}nez\\
		Thomas Nordstr\"om\\
		Thiago Costa Porto\\
		Linus Sunde\\
		Kim-Anh Tran
}

\date{}
\begin{document}

\maketitle

\input{abstract.tex}
\input{glossary.tex}

\tableofcontents

\input{introduction.tex}

\chapter{Preliminaries}
\label{sec:preliminaries}
\input{Preliminaries/Netinf/Prelim-Netinf.tex}
\section{Development Languages}
\input{Preliminaries/Frontend/devlang-frontend.tex}
\input{Preliminaries/Backend/devlang-backend.tex}
\chapter{Goals and Scope}
\label{sec:goals}
\input{Goals-Scope/Goals-Scope-Frontend.tex}
\input{Goals-Scope/Goals-Scope-Backend.tex}

\chapter{Product Description}
\label{sec:product}

\input{Product-Description/Frontend/ProductDesc-frontend.tex}

\input{Product-Description/Backend/ProductDesc-backend.tex}

\chapter{System Architecture}
\label{sec:architecture}

\input{System-Arch/Frontend/SystemArch-frontend.tex}

\section {Backend NetInf NRS}

\input{System-Arch/Backend/SystemArch-backend-overall_design.tex}

\input{System-Arch/Backend/SystemArch-backend-dependencies.tex}

\input{System-Arch/Backend/SystemArch-backend-configurations.tex}

\input{System-Arch/Backend/SystemArch-backend-convergence_layers.tex}

\input{System-Arch/Backend/SystemArch-backend-PNP_database_wrappers.tex}

\input{System-Arch/Backend/SystemArch-backend-video_streaming.tex}

\chapter{Evaluation and testing}
\label{sec:evaluation}
\input{Evaluation/Eval-frontend.tex}
\input{Evaluation/Eval-backend.tex}

\chapter{Conclusions and Future Work}
\label{sec:conclusions}
\input{Conclusions}
\input{Future-Work}

\chapter{Appendix A: Installation instructions}
\section {Frontend}
\input{Appendix-A/App-A-Installation_instructions_frontend.tex}
\section {Backend}
\input{Appendix-A/App-A-Installation_instructions_backend.tex}
\chapter {Appendix B: Maintenance instructions}

\section{Frontend}
\label{sec:Frontend Installation Instructions}
\input{Appendix-B/App-B-Maintenance_instructions_frontend.tex}
\section{Backend}
\input{Appendix-B/App-B-Maintenance_instructions_backend.tex}
\chapter {Appendix C: NetInf Video Streaming Draft}
\input{Appendix-C/NetInf_video_streaming_protocol.tex}
\chapter {Appendix D: License}
\input{Appendix-D/license.tex}

\begin{thebibliography}{99}

\bibitem{netinf}
 A survey of information-centric networking,
 \newblock Ahlgren, B. and Dannewitz, C. and Imbrenda, C. and Kutscher, D. and Ohlman, B.
 \newblock IEEE Communications Magazine, July 2012

 \bibitem{ericsson}
 Ericsson - A world of communication - Ericsson
 \newblock  Retrieved January 15th, 2013, from http://www.ericsson.com/se
 

\bibitem{erlang}
Erlang Programming Language
\newblock Retrieved January 15th, 2013, from http://www.erlang.org/

\bibitem{android}
Android Developers (n.d.). 
\newblock Android Developers. 
\newblock Retrieved January 8th, 2013, from http://developer.android.com

 \bibitem{opennetinf}
C.~Dannewitz, M.~Herlich, E.~Bauer, M.~Becker, F.~Beister, N.~Dertmann,
  R.~Hrestic, M.~Kionka, M.~Mohr, M.~M\"uhe, D.~Murali, F.~Steffen, S.~Stey,
  E.~Unruh, Q.~Wang, and S~Weber.
\newblock OpenNetInf Documentation Design and Implementation.
\newblock Technical Report TR-RI-11-314, University of Paderborn, Sept 2011.
 

\bibitem{ICNarticle} INFORMATION-CENTRIC NETWORKING Kostas Pentikousis et. al. IEEE Communications Magazine, July 2012

\bibitem{otpInAction} Martin Logan, Eric Merritt, and Richard Carlsson. \textsl{Erlang and OTP in Action}. 2010.

\bibitem{4ward} 4WARD project EU. 4WARD project home page. [Online]. http://www.4ward-project.eu/

\bibitem{masterthesis}
Hugo Negrette~Otaola and Miguel Sosa.
\newblock Using Multiple Transport Networks in NetInf Enabled Android Devices.
\newblock Master's thesis, KTH, School of Information and Communication
  Technology (ICT), 2012.

\bibitem{netinfproto}
D.~Kutscher, S.~Farrell, and E.~Davies.
\newblock The NetInf Protocol.
\newblock Internet-Draft draft-kutscher-icnrg-netinf-proto-00.txt, IETF
  Secretariat, Oct 2012.





\bibitem{guice} Google Guice (n.d.). Retrieved January 15, 2013, from http://code.google.com/p/google-guice/

\end{thebibliography}

\end{document}
