The Project Computer Science\footnote{\url{http://www.it.uu.se/edu/course/homepage/projektDV/ht12}} is a university
course at Uppsala University that offers a software project in cooperation with a company. Ericsson Research (\cite{ericsson}) acted as 
the customer for this project whereas the IT department of Uppsala University facilitated us with a project room, software and hardware infrastructure.

The main purpose of this project was to develop a product based on Information-Centric Networking(ICN), as described in \cite{netinf}.
One out of four architectures that realize this concept of ICN is the Network of Information (NetInf, see \cite{netinf}). 
The new idea behind ICN and thus NetInf is to retrieve requested content from any device  instead of retrieving it from a specific host. 
As a result, content can be theoretically downloaded from any number of nearby devices via peer-to-peer. 
This way network congestion could be avoided.

The project group was divided into two teams whereas one team was dedicated for developing the front-end of the 
application whereas the other team was given the task to develop the back-end. The front-end group was called 
LISA (abbreviation for "Look! I see ants!" which sounds like ICNs) and consisted of five members whereas 
the back-end team was named ERNI (Erlang NetInf) and was made up of eight individuals. 

Starting off with the front-end's lose requirement to use NetInf within an application that can communicate with
the back-end's server, the front-end decided to develop a mobile browser called "Elephant". 
Elephant looks like a normal browser from an end-user's perspective. So what differentiates a 
normal browser from the developed one? Instead of using normal host-based networking, a more information-centric networkingapproach is used. 
Many recent papers and research efforts have noted that we should move the Internet 
away from its current reliance on purely point-to-point primitives to designs that make the Internet more data-oriented or content-centric. \cite{ghodsietal}  

Therefore the browser is a proof-of-concept towards a new networking model where Information Objects are in focus.
For the development Ericsson provided Android phones. Thus, Java was the language of choice.

The back-end team developed the Name Resolution Service (NRS, see \cite{netinf}) to perform the back-end operations using Erlang/OTP\cite{erlang}. 
The details of the functionalities developed 
by the front-end and back-end teams can be found in the product report. 

Both teams followed Scrum as the software development methodology. Scrum is a framework structured to support complex product development. Scrum consists of
Scrum Teams and their associated roles, events, artifacts, and rules (\cite{scrumpaper}).
You can find a short description about Scrum and
how we used Scrum in \sect{scrum}.

This document describes in detail the various tools, methodology and equipments we used to achieve our goals. 
